\documentclass[a4paper,22pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[T2A]{fontenc}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\usepackage[english]{babel}
\usepackage{ragged2e}
\usepackage{graphicx}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% %-----------------------------
% %%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Sergei Druzhkov}} &
  \href{https://github.com/DrSergei}{GitHub:~github.com/DrSergei}\\
  \href{mailto:serzhdruzhok@gmail.com}{Email: serzhdruzhok@gmail.com}\ & 
  \href{https://t.me/SergeiDruzhkov}{Telegram:~~~@SergeiDruzhkov}\\
  \href{https://orcid.org/0009-0000-6835-2844}{ORCID: 0009-0000-6835-2844} & Mobile:~~~~~~+7-900-521-97-42 \\
  Date of Birth: 23.11.2002 & City:~~~~~~~~~~Saint Petersburg \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SPbSU (Department of Mathematics and Computer Sciences)}{Saint Petersburg, Russia}
      {Applied Mathematics and Computer Science (Modern Programming)}{2021 -- 2025}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{GPA:} 4.93 (out of 5.00)}}}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Thesis:} Clone detection and automatic refactoring of Lua programs for network devices}}}
    \resumeSubheading
      {ITMO (Institute of Applied Computer Sciences)}{Saint Petersburg, Russia}
      {Applied Mathematics and Computer Science (Programming and Artificial Intelligence)\hspace{-50pt}}{2025 -- 2027}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{GPA:} 5.00 (out of 5.00)}}}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Thesis:} ---}}}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Skills Summary}
    \resumeSubHeadingListStart
        \resumeSubItem{Languages}{~~~~~~~~~~~C/C++, SQL, Go, TypeScript, Lua, Python}
        \resumeSubItem{Technologies}{~~~~~~~~LLVM, SQLite, CMake, Make, Git, Docker, \LaTeX}
        \resumeSubItem{Communication}{~~~Russian (Native), English (Upper-Intermediate)}
    \resumeSubHeadingListEnd
\vspace{-5pt}

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Huawei Russian Research Institute}{}
    {Research engineer}{April 2022 -- Present}
        \resumeItemListStart
        \resumeItem{Engineering activity}{Development of high-performance applications based on research and classical results, as well as their support and integration into the company's existing ecosystem.}
        \resumeItem{Research activity}{Analysis of academic publications and conducting own research based on them in the field of program analysis and developer tools.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Static analysis tool for C/C++}{
\begin{itemize}
\vspace{-5pt}
\item Interprocedural taint analysis of C/C++ programs based on LLVM/Clang for large codebases (>20 MLOC).
\vspace{-3pt}
\item Development of domain-specific checks and solutions for internal company projects.
\vspace{-3pt}
\item Research on applicability of graph databases (ArangoDB, Neo4j) for program analysis tasks.
\vspace{-3pt}
\end{itemize}
}
\resumeSubItem{Lua minifier}{
\begin{itemize}
\vspace{-5pt}
\item Classic code reduction techniques: removing whitespace, comments, and blank lines; renaming variables and labels; dead code elimination and other language-specific code transformations.
\vspace{-3pt}
\item Ability to find and remove duplicate code fragments.
\vspace{-3pt}
\item Code size reduction by more than 2 times. Runtime under 2 minutes on a large codebase (5 MLOC).
\vspace{-3pt}
\end{itemize}
}
\resumeSubItem{Debugging tools for C/C++}{
\begin{itemize}
\vspace{-5pt}
\item Support for debugging C/C++ code with GDB/LLDB on Linux/Windows/HarmonyOS.
\vspace{-3pt}
\item Remote device debugging via SSH and Telnet.
\vspace{-3pt}
\item Advanced debugging techniques (child process debugging, deadlock detector, thread fuzzer, memory debugging, etc.).
\vspace{-3pt}
\item Over 1500 regular users inside the company.
\vspace{-3pt}
\end{itemize}
}
\vspace{2pt}
\resumeSubItem{Debug Agent}{
\begin{itemize}
\vspace{-3pt}
\item MCP server based on VS Code API for interacting with the debugging subsystem with full integration into VS Code UI.
\vspace{-3pt}
\item MCP server for CLI agents to work with debuggers such as GDB, LLDB, Delve, etc. via DAP.
\vspace{-3pt}
\end{itemize}
}
\vspace{2pt}
\resumeSubHeadingListEnd

%-----------Awards-----------------
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
\item {Participant of the All-Russian Olympiad in Mathematics --- 2019 (71/130)}
\vspace{-5pt}
\item {Prize-winner of the All-Russian Olympiad in Mathematics --- 2021 (44/166)}
\vspace{-5pt}
\item {Prize-winner of the All-Russian Olympiad in Economics --- 2019 (13/77), 2021 (43/135)}
\vspace{-5pt}
\item {Prize-winner of the Regional Mathematics Olympiad for university students of Saint Petersburg --- 2022 (12/122)}
\vspace{-5pt}
\item {Prize-winner of ``I am a Professional'' in ``Mathematics'' --- 2025}
\vspace{-5pt}
\item {Winner of the Siberian Mathematical Olympiad --- 2025 (8/378)}
\vspace{-5pt}
\item {Prize-winner of North Countries Universities Mathematical Competition --- 2026 (24/149)}
\end{description}


\vspace{-5pt}
\section{Other Experience}
\begin{description}[font=$\bullet$]
\item {Teacher at Kirov Summer Multidisciplinary School (LMSH) --- 2021}
\vspace{-5pt}
\item {Jury of the municipal and regional stage of the All-Russian Olympiad in Mathematics (Kirov) --- 2021--2025}
\vspace{-5pt}
\item {Jury of the Saint Petersburg Mathematical Olympiad --- 2022--2026}
\end{description}

\end{document}
